First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-19 MY_PUBLICATIONS/PRL/draft_v2/prl.tex
update
updated

\begin{abstract}
  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  for neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c at several fixed neutron recoil angles ($\theta_{nq}$)
  with respect to the 3-momentum transfer, $\vec{q}$. At neutron angles of 35 and 45 degrees final state interactions (FSIs) as well as
  meson exchange currents (MECs) and isobar configurations (ICs) are expected to be suppressed and the plane wave impulse
  approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent theoretical
  calculations where significant disagreement at very high missing momenta has been observed.
\end{abstract}

>>>>

\begin{abstract}
  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  reaching neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c. The data have been obtained at fixed neutron recoil angles
($\theta_{nq}$) of 35$^\circ$ and 45$^\circ$  with respect to the 3-momentum
transfer, $\vec q$. At these kinematic settings final state interactions (FSIs),
meson exchange currents (MECs) and isobar configurations (ICs) are expected to 
be suppressed and the plane wave impulse approximation (PWIA) provides the
dominant cross section contribution. The new data are compared to recent
theoretical calculations where a significant disagreement at very high
missing momenta has been observed.

\end{abstract}
